\documentclass{resume}

\usepackage[left=0.7in,top=0.5in,right=0.7in,bottom=0.5in]{geometry} % Document margins
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\setlist{nosep}

\name{Surajeet Bharati} % Your name
\address{9679176083 $\scriptstyle\bullet$ surajeet01@gmail.com $\scriptstyle\bullet$ \href{https://linkedin.com/in/surajeetbharati}{linkedin://surajeetbharati}} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{\href{https://mentor.com}{Siemens EDA}}{Lead Member Technical Staff}{August 2017 - Present}{Language used - C}{Kolkata, India}
\item Worked on Replaced the skeleton data structure used for internal representation of an elaborated HDL design from Tree to Graph. Achieved 12x improvement time and memory requirement for several customer designs.
\item Designed and implemented several parts of the Global Analysis module, used for property propagation throughout elaborated HDL design which in terms helps to generate optimized byte-code.
\item Working on performance improvement of the Global Analysis module through independently figuring out performance bottlenecks in the system and then modifying relevant implementation. Improved run-time of the module up to 4x for some customer designs.
\end{rSubsection}

\begin{rSubsection}{\href{http://www.polarisnetworks.net/}{Polaris Networks}}{Software Development Engineer}{July 2015 - July 2017}{Languages/Frameworks used - C, C++, C\#, Qt}{Kolkata, India}
\item Worked on Protocol stack development for core features of \href{https://polarisnetworks.net/lte_emulators.html}{MCE Emulator} of LTE network.
\item Developed several parts of the software modules and user interface of \href{https://www.anritsu.com/en-us/test-measurement/products/spider}{Anritsu Spider}, an automated, scalable Radio Frequency emulation platform.
\item Co-designed and implemented the console and relevant server side APIs of \href{https://polarisnetworks.net/functional-testers.html}{Polaris Functional Tester}, a server-client architecture based tool used for compliance testing of LTE network nodes.
\end{rSubsection}

\end{rSection}

%---------------------------------------------------------------------------------------
%   PROJECTS
%---------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{Development of Filters for Transcription between Documents}{}{July 2014 - April 2015}{Languages/Frameworks used - Java Servlet, Flex, Bison, php}{IIEST, Shibpur}
\item Designed and implemented filters for transcription of typed Bengali documents into English scripts and vice-versa using Java Servlet and Lexical Analyzer.
\end{rSubsection}

\begin{rSubsection}{Automated Video Classification \& Categorization}{}{May-July, 2014}{Language used - Matlab}{ISI, Kolkata}{}
\item Automated the process of categorizing a video especially a movie through performing pixel-level comparison of consecutive frames using existing Image Processing algorithms.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Indian Institute of Engineering Science \& Technology, Shibpur} \hfill May 2015 \\ 
{\em BE, Computer Science \& Technology} \hfill {\em CGPA: 8.74 / 10} \smallskip \smallskip \\
{\bf Burdwan Municipal High School, Burdwan} \hfill May 2011 \\ 
{\em Higher Secondary, Science} \hfill {\em 84.6\%} \\  

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Programming Skill}
\renewcommand\labelitemi{$\cdot$}
\begin{itemize}[leftmargin=0em]
  \item Over 5000 lines of code: C, C++
  \item Over 1000 lines of code: C\#, Java
  \item Familiar with: Tcl, Shell scripting, Qt, php
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
